---
title: "Data 605 - Assignment 5"
author: "Habib Khan"
date: "March 1, 2020"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

# Introduction 

Choose independently two numbers B and C at random from the interval [0, 1] with uniform density. Prove that B and C are proper probability distributions.
Note that the point (B,C) is then chosen at random in the unit square.



```{r}
B <- runif(1000)
C <- runif(1000)
```


## Checking if B and C are probability distributions

```{r}
hist(B, probability = TRUE)
hist(C, probability = TRUE)
```

Both B and C are probability distributions and hence we can go further with the analysis.


## (a) B + C < 1/2
```{r}

Z <- B + C

probability <- length(Z[Z<= .5])/1000
probability
```

## (b) BC < 1/2

```{r}
Z <- B*C

probability <- length(Z[Z<= .5])/1000
probability
```

## (c) |B − C| < 1/2


```{r}
Z <- abs(B-C)

probability <- length(Z[Z<= .5])/1000
probability
```


## (d) max{B,C} < 1/2.

```{r}
maxx <- matrix(c(B,C),1000,2)
Z <- apply(maxx, 1, max)

probability <- length(Z[Z<= .5])/1000
probability
```


## (e) min{B,C} < 1/2

```{r}
minn <- matrix(c(B,C),1000,2)
Z <- apply(minn, 1, min)

probability <- length(Z[Z<= .5])/1000
probability
```












